FantasticLamp: quantifying genomic edits with genome variation graphs

### 2024-02-02 paper/main.tex
funding and conflict of interest

\section*{Funding}

@@

>>>>

\section*{Funding}
The authors gratefully acknowledge support from National Institutes of Health/NIDA U01DA047638 (E.G.), National Institutes of Health/NIGMS R01GM123489 (E.G.), and NSF PPoSS Award \#2118709 (E.G.), and the Center for Integrative and Translational Genomics (E.G. and C.S.).

@@

\section*{Conflict of interest}
The authors declare that they have no conflicts of interest.
